
\documentclass{IOS-Book-Article}

\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{soul}\setuldepth{article}


\usepackage{algpseudocode}

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{CJKutf8}
\usepackage{graphicx,pstricks}
\usepackage{ulem}
\usepackage{tikz}
\usepackage{algpseudocode}

\usepackage{moreverb}
\usepackage{subcaption}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage[percent]{overpic}
\usepackage{textcomp}
\usepackage{subfiles}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{algorithmicx}
\usepackage{ctable}
\usepackage{txfonts}
\usepackage{palatino}
\begin{comment}
\end{comment}
\usepackage{csquotes}
\renewcommand{\mkbegdispquote}[2]{\itshape}
\usepackage{textcomp}
\usepackage{url}
% fg settings
\newcommand{\setttsize}[1]{\def\ttsize{#1}}%
\newcommand{\mvmtmldir}[0]{/Users/psychomugs/projects/mvmt_ml_results/blossom_face/}
% ubicomp settings
\newcommand{\tablevspace}[0]{-.3cm}
\newcommand{\figwidth}[0]{0.9}
% \newcommand{\ms}[1]{\textcolor{red}{$<$MS: #1$>$}}
\newcommand{\ms}[1]{\textcolor{red}{#1}}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\def\hb{\hbox to 11.5 cm{}}

\begin{document}
\begin{CJK*}{UTF8}{min}

\pagestyle{headings}
\def\thepage{}

\begin{frontmatter}              % The preamble begins here.


\title{
At Least, Be Human:\\
Humanizing the Robot as a\\
Medium for Communication}
% \title{
% At Least, Be Human: Humanizing the\\
% Robot as a Medium for Communication}

\markboth{}{August 2022\hb}

\author{\fnms{Michael} \snm{Suguitan}%
\thanks{E-mail:
mjs679@cornell.edu}}

\runningauthor{M. Suguitan}
\address{Cornell University}

\begin{abstract}
A central tenet of human-robot interaction research is to humanize social robots as collaborators and companions.
Literal approaches to humanizing, either through human-like behaviors or humanoid embodiments, pose technological and social challenges that have precluded adoption of robots in everyday contexts.
Even if convincingly humanized robots could be achieved, human-robot interaction may enable an escapism that diminishes our capacity for human-human interaction.
I propose to avoid these pitfalls by humanizing the robot as a medium for communication through accessibility.
Accessibility humanizes technology by makings inner workings visible and familiar to human users, promoting understanding of technological processes and imperfections.
Accessibility also enables broader demographics of lay users to become involved with robotics, enabling communication \textit{through} robots, from development processes (e.g. physical and behavioral design) to applications (e.g. telepresence).
I use the open-source Blossom social robot as an extended case study of this approach, and detail its technical implementations and research deployments.
The goal of this work is to present accessibility as a way to humanize robots while enabling robot-mediated communication for human-human interaction.
\end{abstract}

\begin{keyword}
human-robot interaction\sep robot-mediated communication\sep\\
accessibility\sep design\sep artificial intelligence\sep telepresence
\end{keyword}
\end{frontmatter}
\markboth{August 2022\hb}{August 2022\hb}
\input{./robophilosophy/robophilosophy-1-intro}
\input{./robophilosophy/robophilosophy-2-implementation}
\input{./robophilosophy/robophilosophy-3-conclusion}

\bibliographystyle{ieeetr}
\bibliography{master.bib}

\end{CJK*}
\end{document}
